---
title: "balselr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{balselr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(balselr)
```


## Read in some data

Read in a vcf ([Variant Call Format][https://en.wikipedia.org/wiki/Variant_Call_Format]) file:

```{r, echo=T, eval=F}
read_vcf(x=system.file("balselr","example.vcf"))
```


## Prepare `ncd1` input file

This is an example which shows how to parse a vcf file and output an input file for `ncd1`:

```{r, echo=T, eval=F}
prep_my_ncd1_file<-parse_vcf(
        infile = system.file(package = "balselr", "example.vcf"),
        n0 = 108,
        type = "ncd1"
)
```

This is an example which shows how to parse an R object made from a vcf file and output an input file for `ncd1`:

```{r, echo=T, eval=F}
prep_my_ncd1_file2<-parse_vcf(
        vcf_data = vcf_obj),
        n0 = 108,
        type = "ncd1"
)
```



Run `ncd1` with a 3000 basepair window and a minimum of 8 informative sites per window using 2 cores and a target frequency of 0.5:

```{r, echo=T, eval=F}

res1<-ncd1(x=prep_my_ncd1_file, tf=0.5, w=3000, ncores=2, minIS=8)
res1
```


Make the minIS filter less restrictive and the window smaller:


```{r, echo=T, eval=F}
res2<-ncd1(x=prep_my_ncd1_file, tf=0.5, w=2000, ncores=2, minIS=2)
res2
```

## Prepare `ncd2` input file

This is an example which shows how to parse a vcf file and output an input file for `ncd1`; use 4 individuals for the outgroup:

```{r, echo=T, eval=F}
prep_my_ncd1_file<-parse_vcf(
        infile = system.file(package = "balselr", "example.vcf"),
        n0 = 108,
        n1 = 4,
        type = "ncd2"
)
```

This is an example which shows how to parse an R object made from a vcf file and output an input file for `ncd1`; use only one individual for the outgroup:

```{r, echo=T, eval=F}
prep_my_ncd2_file2<-parse_vcf(
        vcf_data = vcf_obj),
        n0 = 108,
        n1 = 1,
        type = "ncd2"
)
```



Run `ncd2` with a 3000 basepair window and a minimum of 8 informative sites per window using 2 cores and a target frequency of 0.5:

```{r, echo=T, eval=F}

res1<-ncd2(x=prep_my_ncd2_file, tf=0.5, w=3000, ncores=2, minIS=8)
res1
```


Make the minIS filter less restrictive and the window smaller:


```{r, echo=T, eval=F}
res2<-ncd2(x=prep_my_ncd2_file, tf=0.5, w=2000, ncores=2, minIS=2)
res2
```
